Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-17 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:17	13:05:27	(Mon17.Aug)

Let the receiver be an $M$ element uniform linear array. The Assume that the array channels are digitally delayed to focus at a pixel with azimuth angle $\theta$ and range sample $n$, such that the delayed data from the $m$th channel can be expressed as $x_m[\theta,n]$. To simplify notation, we make the dependence on $\theta$ implicit from now on.

>>>>

Let the receiver be an $M$ element uniform linear array. Call the the data from the $m$th channel $x_m[\theta,n]$, where the azimuth angle $\theta$ and range sample $n$ is the focus point. To simplify notation, we make the dependence on $\theta$ implicit from now on.
